---
title: "HW Question #14"
author: "Carlisha Hall"
date: "March 12, 2019"
output: github_document
---

###HW Question #14. Write a function to calculate the ANNUAL (calendar year) mean, median, max and min of all sites that have “San” or “Santa” in their name.

```{r}
library(stringr)
library(lubridate)
colnames(loc)[1] <- "site"
daily.site <- daily %>%
  left_join(loc, by = "site")

#Create object with variable of interest
daily.site1<-select(daily.site, site, date, o3, 'Site Name') 

#Filter varibales of interest 
Daily1.Filter<-daily.site1 %>% 
  filter(str_detect(`Site Name`, "(San|Santa)"))
 

#components for function
Daily1.Filter<-daily.site1 %>% 
  filter(str_detect(`Site Name`, "(San|Santa)"))
  
 AnnualSum1 <- group_by(Daily1.Filter, # data_frame object
                          year = year(date)) %>% summarize(mean(o3, na.rm=TRUE),
              median(o3, na.rm=TRUE), 
              max(o3, na.rm=TRUE),
              min(o3, na.rm=TRUE)) 


#Function 
Annual.Sum<-function(x) {

Daily1.Filter<-(x) %>% 
filter(str_detect(`Site Name`, "(San|Santa)"))
AnnualSum1 <- group_by(Daily1.Filter, # data_frame object
                          year = year(date)) %>% summarize(mean(o3, na.rm=TRUE),
              median(o3, na.rm=TRUE), 
              max(o3, na.rm=TRUE),
              min(o3, na.rm=TRUE)) 
}
view(Annual.Sum(daily.site1))
```

###HW Question #15. Write a function to caculate the annual daily mean (what is the annual mean of the daily mean?). Apply that function to Merced County. What is the annual daily mean of o3 for Merced County? Report your results in quantititive format (i.e., prose, or a table), and in visual format (i.e., a graph).

```{r}
library(stringr)
library(lubridate)
colnames(loc)[1] <- "site"
daily.site <- daily %>%
  left_join(loc, by = "site")

#Create object with variable of interest
daily.site2<-select(daily.site, site, date, o3, 'County Name') 

#Filter varibales of interest 
Daily2.Filter<-daily.site2 %>% 
  filter(str_detect(`County Name`, "(^Merced$)"))


#components for function
Daily2.Filter<-daily.site2 %>% 
filter(str_detect(`County Name`, "(^Merced$)"))
  
dailySum <- group_by(Daily2.Filter,  # data_frame object
day = day(date), year(date)) %>% summarize(mean(o3, na.rm=TRUE)) 



Merced.Daily<-function(x) {
  
  Daily2.Filter<-(x) %>% 
filter(str_detect(`County Name`, "(^Merced$)"))

  dailySum <- group_by(Daily2.Filter,  # data_frame object
day = day(date), year(date)) %>% summarize(mean(o3, na.rm=TRUE)) 
}
view(Merced.Daily(daily.site2))

mydata<-Merced.Daily(daily.site2)


library(ggplot2)
ggplot(data = mydata, aes((x = mydata$`year(date)`), (y = mydata$`mean(o3, na.rm = TRUE)`))) + geom_line(color = "#00AFBB", size = 3)


```

